Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-06-12 manuscript/supplementary_information.Rmd
aesthetic changes to supplementary figures

  # build plot
  plot <- ggplot(data = data.frame(effectSize = seq(0,1,.01), precision = vector), aes(x = effectSize, y = precision)) +
    geom_line(colour = 'darkblue', size = 1) +
    theme_classic() +
    ylab('Margin of error') +
    xlab('Effect size') +
    scale_x_continuous(expand = c(0.01, 0), limits = c(0,1)) +
    scale_y_continuous(expand = c(0.01, 0), 
                       limits = c(0,round(max(vector),2)),
                       breaks = seq(0,round(max(vector),2),0.05),
                       labels = seq(0,round(max(vector),2),0.05))

@@

locusPlot <- rbind(locus_before, locus_after) %>%
  select(-analysis) %>%
  rename('analysis\nspecification' = 'specification') %>%
  gather(locus, count, typo:`analysis\nspecification`, factor_key=TRUE) %>%
  mutate(status = factor(status, c('resolved', 'unresolved')),
         locus = factor(locus, c('analysis\nspecification', 'unidentified', 'data', 'typo'))) %>%
  ggplot(aes(group = status, fill = status, x = locus, y = count)) +
    geom_col(width = .8) +
    scale_fill_manual(name = 'status', values=c('grey', 'gray20'), labels = c('resolved after\nauthor involvement', 'unresolved')) +
    xlab('locus of non-reproducibility') +
    theme_minimal() +
    theme(panel.grid.major.x = element_blank()) +
  ylim(0,20)
```

@@

```{r}
timePlot <- data_articles %>%
  # compute total time to complete (TTC) in hours
  mutate(activeTTC = (pilotTTC + copilotTTC)/60,
         finalOutcome = fct_relevel(finalOutcome,
    "Reproducible\nwithout author\ninvolvement",
    "Reproducible\nwith author\ninvolvement",
    "Not reproducible\nwith author\ninvolvement",
    "Not reproducible\nwithout author\ninvolvement"
    )) %>%
  ggplot(aes(x=activeTTC, fill=finalOutcome)) +
    geom_histogram(colour = 'black', bins = 15) +
    facet_grid(rows = 'finalOutcome') +
    xlab("estimated active work hours") +
    ylab("number of reproducibility checks") +
    theme_minimal() +
    theme(panel.grid.minor.y = element_blank()) +
    scale_fill_manual(values = c(green, yellow, blue, purple), guide=F) +
    scale_y_continuous(breaks = c(0,1,2,3), labels = c('0','1','2','3'))
```

>>>>

  # build plot
  plot <- ggplot(data = data.frame(effectSize = seq(0,1,.01), precision = vector), aes(x = effectSize, y = precision)) +
    geom_line(colour = 'black', size = 1) +
    theme_classic(base_size = 12) +
    theme(axis.text = element_text(colour = 'black')) +
    ylab('Margin of error') +
    xlab('Effect size') +
    scale_x_continuous(expand = c(0.01, 0), limits = c(0,1)) +
    scale_y_continuous(expand = c(0.01, 0), 
                       limits = c(0,round(max(vector),2)),
                       breaks = seq(0,round(max(vector),2),0.05),
                       labels = seq(0,round(max(vector),2),0.05))

@@

locusPlot <- rbind(locus_before, locus_after) %>%
  select(-analysis) %>%
  rename('analysis\nspecification' = 'specification') %>%
  gather(locus, count, typo:`analysis\nspecification`, factor_key=TRUE) %>%
  mutate(status = factor(status, c('resolved', 'unresolved')),
         locus = factor(locus, c('analysis\nspecification', 'unidentified', 'data', 'typo'))) %>%
  ggplot(aes(group = status, fill = status, x = locus, y = count)) +
    geom_col(width = .8) +
    scale_fill_manual(name = 'status', values=c('grey', 'gray20'), labels = c('resolved after\nauthor involvement', 'unresolved')) +
    xlab('locus of non-reproducibility') +
    theme_minimal(base_size =  12) +
    theme(axis.text = element_text(colour = 'black'),
          panel.grid.major.x = element_blank()) +
  ylim(0,20)
```

@@

```{r}
timePlot <- data_articles %>%
  # compute total time to complete (TTC) in hours
  mutate(activeTTC = (pilotTTC + copilotTTC)/60,
         finalOutcome = fct_relevel(finalOutcome,
    "Reproducible\nwithout author\ninvolvement",
    "Reproducible\nwith author\ninvolvement",
    "Not reproducible\nwith author\ninvolvement",
    "Not reproducible\nwithout author\ninvolvement"
    )) %>%
  ggplot(aes(x=activeTTC, fill=finalOutcome)) +
    geom_histogram(colour = 'black', bins = 15) +
    facet_grid(rows = 'finalOutcome') +
    xlab("estimated active work hours") +
    ylab("number of reproducibility checks") +
    theme_minimal(base_size = 12) +
    theme(axis.text = element_text(colour = 'black'),
          panel.grid.minor.y = element_blank(),
          strip.text.y = element_text(size = 9)) +
    scale_fill_manual(values = c(green, yellow, blue, purple), guide=F) +
    scale_y_continuous(breaks = c(0,1,2,3), labels = c('0','1','2','3'))
```
